Star-galaxy Classification Using Deep Convolutional Neural Networks

### 2016-10-04 paper/main.tex
add footnote on qsos

With machine learning, we can use algorithms to automatically create
accurate source catalogs with well-calibrated posterior probabilities.
Machine learning techniques have been a popular tool
in many areas of astronomy~\citep{ball2008robust,
banerji2010galaxy,
carrascokind2013tpz,
ivezic2014statistics,
kamdar2016machine1}. 
Artificial neural networks were first applied to the problem of star-galaxy
classification in the work of \citet{odewahn1992automated},
and they have become a core part of the astronomical image processing software
\texttt{SExtractor}~\citep{bertin1996sextractor}.
Other successfully implemented examples of applying machine learning to
the star-galaxy classification problem include decision 
trees~\citep{weir1995automated,suchkov2005census,ball2006robust,sevilla2015effect}, 
Support Vector Machines~\citep{Fadely2012}, and
classifier combination strategies~\citep*{kim2015hybrid}.

@@

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.
\changed{
We exclude quasars, as they clearly are neither stars nor galaxies and many of
them have one or more saturated pixels in the images.
}
We exclude some bad photometric observations as follows.
We consider only objects
with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
the half-light radius in the $r$ band is less than 30 arc seconds
as measured by the exponential and de Vaucouleurs light profiles;
the error on the spectroscopic redshift measurement is less than 0.1; and
the spectroscopic redshift is less than 2.

>>>>

With machine learning, we can use algorithms to automatically create
accurate source catalogs with well-calibrated posterior probabilities.
Machine learning techniques have been a popular tool
in many areas of astronomy~\citep{ball2008robust,
banerji2010galaxy,
carrascokind2013tpz,
ivezic2014statistics,
kamdar2016machine1}. 
Artificial neural networks were first applied to the problem of star-galaxy
classification in the work of \citet{odewahn1992automated},
and they have become a core part of the astronomical image processing software
\texttt{SExtractor}~\citep{bertin1996sextractor}.
Other successfully implemented examples of applying machine learning to
the star-galaxy classification problem include decision 
trees~\citep{weir1995automated,suchkov2005census,ball2006robust,vasconcellos2011decision,sevilla2015effect}, 
Support Vector Machines~\citep{Fadely2012}, and
classifier combination strategies~\citep*{kim2015hybrid}.

@@

Using the CasJobs server, we randomly select a total of 65,000 sources,
which are either stars or galaxies.\footnote{
\changed{
We exclude objects that clearly are neither stars nor galaxies.
Most of the excluded objects are QSOs or quasars.
Quasars appear as point sources, rather than resolved sources similar to
galaxies,
and many of them have one or more saturated pixels in the images.
They are also different from galaxies because of their intrinsic variability on
a wide range of time scales, which may be due to variation in the accretion rate
or instabilities of the accretion disk around the black hole
\citep{popovic2012photocentric}.
However, unlike any known stars, their spectra show strong and broad emission
lines.
Thus, many studies exclude quasars in the binary star-galaxy classification
scheme
\citep[\eg][]{vasconcellos2011decision,Fadely2012}.
Expanding the historical star-galaxy classification problem to include
other classes may have advantanges~\citep{ball2006robust}, and we defer
the results of this multi-class problem to a future paper.}
}
We exclude some bad photometric observations as follows.
We consider only objects
with no warning flags in the spectroscopic measurement (\texttt{zWarning = 0});
the half-light radius in the $r$ band is less than 30 arc seconds
as measured by the exponential and de Vaucouleurs light profiles;
the error on the spectroscopic redshift measurement is less than 0.1; and
the spectroscopic redshift is less than 2.
